Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-22 Draft.Rmd
pred elim

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(caret)
library(plotROC)

@@

# Create standardize train data for kNN and PCA

@@

## Predictor Reduction
```{r}
# Scale dataset

@@

## Models 
```{r Lin Regr.}
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

@@

# Scale the training data for k-NN model
train_scaled = train |> dplyr::select(where(is.numeric)) |> mutate(across(fips:aod, scale)) |> cbind(state=train$state,county=train$county,city=train$city)

>>>>

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(caret)
library(plotROC)
library(randomForest)

@@

# Create standardize train data for kNN and PCA
# excl. id and value
train_scaled = train[,3:50] |> dplyr::select(where(is.numeric)) |> mutate(across(fips:aod, scale)) |> cbind(state=train$state,county=train$county,city=train$city)

@@

## Predictor/Feature Selection
```{r}
# Use Random Forest for variable selection
rfmodel = randomForest(value~., data=train[,2:50])
import=as.data.frame(importance(rfmodel)) |> arrange(desc(IncNodePurity))
import=tibble::rownames_to_column(import, 'variables')
# Now from this list, you can select the variables. Mostly, the top 20 variables are what we select. However, this is just an indicative value and may vary based upon the problem.

# take top 20 important variables
import20 = import[1:20,]

# Use Information Gain for variable selection
library(MASS)

fit_lm = lm(value~, data=train)

stepAIC(fit_lm, direction="backward", trace=FALSE)
stepAIC(fit_lm, direction="forward", trace=FALSE)
stepAIC(fit_lm, direction="both", trace=FALSE)

# Use Recursive Feature Elimination method
set.seed(123)
cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')

profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)

# Use Lasso for variable selection X
y=train[,2]

library(glmnet)
feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)

as.matrix(coef(features,features$lambda.min))

# Scale dataset

@@

## Models 
```{r}
set.seed(123)
library(party)
# fit randfom forest and get var. importance based on mean decr. in accuracy
train_num = train[,2:50] |> dplyr::select(where(is.numeric))
cf1 = cforest(value ~ ., data=train_num, control=cforest_unbiased(mtry=2, ntree=50))
# adj for corr. btw predictors
varimp(cf1, conditional=TRUE)
# more robust towards class imbalance
varimpAUC(cf1)

```{r Lin Regr.}
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

imp = varImp(model1, scale=FALSE)

@@

# Scale the training data for k-NN model in wrangling
